---
title: "Homework 3"
subtitle: "Submission 1, Spring 2026"
author: "Sophie Kim"
format:
  pdf:
    output-file: "Kim-s-hwk3-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

```{r}
#| include: false
library(tidyverse)
library(stringr)
library(readr)
library(fs)
library(ggplot2)
library(dplyr)
library(broom)
library(tidyr)
```

```{r}
#| include: false
options(repos = c(CRAN = "https://cloud.r-project.org"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, scales, data.table)

install.packages("knitr", lib="~/R/x86_64-conda-linux-gnu-library/4.3")
install.packages("rmarkdown", lib="~/R/x86_64-conda-linux-gnu-library/4.3")
```

```{r}
#| include: false
data.2010 <- read_csv("..//data/data-2010.csv")
data.2011 <- read_csv("..//data/data-2011.csv")
data.2012 <- read_csv("..//data/data-2012.csv")
data.2013 <- read_csv("..//data/data-2013.csv")
data.2014 <- read_csv("..//data/data-2014.csv")
data.2015 <- read_csv("..//data/data-2015.csv")
```

```{r}
#| include: false
fix_type <- function(df) {
  df$org_parent <- as.character(df$org_parent)
  df
}

data.2011 <- fix_type(data.2011)
```

```{r}
#| include: false
combined <- bind_rows(
  data.2010,
  data.2011,
  data.2012,
  data.2013,
  data.2014,
  data.2015
) %>%
  mutate(mkt_share = avg_enrollment / avg_enrolled)
```

```{r}
#| include: false
colnames(combined)
```



```{r}
#| echo: false
#| warning: false

summary_table <- combined %>%
  group_by(year) %>%
  summarise(
    `Mean Star Rating` = round(mean(Star_Rating, na.rm = TRUE), 2),
    `Mean Enrollments` = round(mean(avg_enrollment, na.rm = TRUE), 2),
    `Mean Market Share` = round(mean(mkt_share, na.rm = TRUE), 4),
    `Total Plans` = n()
  )

print(summary_table)
```

# Problem 2

```{r}
#| echo: false
#| warning: false

summary_no_rating <- combined %>%
  filter(is.na(Star_Rating)) %>%
  group_by(year) %>%
  summarise(
    `Mean Enrollments` = round(mean(avg_enrollment, na.rm = TRUE), 2),
    `Mean Market Share` = round(mean(mkt_share, na.rm = TRUE), 4),
    `Total Plans` = n()
  )

print(summary_no_rating)
```

# Problem 3

```{r}
#| echo: false
#| warning: false

combined %>%
  filter(year %in% c(2010, 2012, 2015), !is.na(Star_Rating)) %>%
  mutate(year = as.factor(year)) %>%
  ggplot(aes(x = as.factor(Star_Rating))) +
  geom_bar() +
  facet_wrap(~ year) +
  labs(
    title = "Distribution of Star Ratings in 2010, 2012, and 2015",
    x = "Star Rating",
    y = "Number of Plans"
  ) +
  theme_minimal()
```

# Problem 4

```{r}
#| include: false
combined <- combined %>%
  mutate(
    star_3   = as.integer(partc_score == 3),
    star_35  = as.integer(partc_score== 3.5),
    star_4   = as.integer(partc_score == 4),
    star_45  = as.integer(partc_score >= 4.5)
  )

results_list <- list()

for(yr in 2010:2015){
  cat("\nYear:", yr, "\n")
  ols <- lm(mkt_share ~ star_3 + star_35 + star_4 + star_45, 
            data = combined %>% filter(year == yr, !is.na(partc_score), !is.na(mkt_share)))
  print(summary(ols))
}
```

```{r}
#| echo: false
#| warning: false

results_list <- list()

for(yr in 2010:2015){
  ols <- lm(mkt_share ~ star_3 + star_35 + star_4 + star_45, 
            data = combined %>% filter(year == yr, !is.na(partc_score), !is.na(mkt_share)))
  results_list[[as.character(yr)]] <- coef(ols)
}

ols_table <- as.data.frame(results_list)
colnames(ols_table) <- c("2010", "2011", "2012", "2013", "2014", "2015")
rownames(ols_table) <- c("Intercept (≤2.5 stars)", "3 Stars", "3.5 Stars", "4 Stars", "4.5+ Stars")

print(round(ols_table, 4))
```

# Problem 5

filter first

```{r}
#| include: false
ma.2010 <- data.2010 %>%
  filter(!is.na(breastcancer_screen), !is.na(rectalcancer_screen),
         !is.na(cv_diab_cholscreen), !is.na(glaucoma_test), !is.na(monitoring),
         !is.na(flu_vaccine), !is.na(pn_vaccine), !is.na(physical_health),
         !is.na(mental_health), !is.na(osteo_test), !is.na(physical_monitor),
         !is.na(primaryaccess), !is.na(osteo_manage), !is.na(diab_healthy),
         !is.na(bloodpressure), !is.na(ra_manage), !is.na(copd_test), !is.na(bladder),
         !is.na(falling), !is.na(nodelays), !is.na(doctor_communicate),
         !is.na(carequickly), !is.na(customer_service),
         !is.na(overallrating_care), !is.na(overallrating_plan),
         !is.na(complaints_plan), !is.na(appeals_timely), !is.na(appeals_review),
         !is.na(leave_plan), !is.na(audit_problems), !is.na(hold_times),
         !is.na(info_accuracy), !is.na(ttyt_available)) %>%
  mutate(
    raw_rating = rowMeans(cbind(breastcancer_screen, rectalcancer_screen,
                                cv_diab_cholscreen, glaucoma_test, monitoring,
                                flu_vaccine, pn_vaccine, physical_health,
                                mental_health, osteo_test, physical_monitor,
                                primaryaccess, osteo_manage, diab_healthy,
                                bloodpressure, ra_manage, copd_test, bladder,
                                falling, nodelays, doctor_communicate,
                                carequickly, customer_service,
                                overallrating_care, overallrating_plan,
                                complaints_plan, appeals_timely, appeals_review,
                                leave_plan, audit_problems, hold_times,
                                info_accuracy, ttyt_available))
  )

# Check thresholds
ma.2010 %>%
  select(raw_rating, partc_score) %>%
  filter(!is.na(partc_score)) %>%
  group_by(partc_score) %>%
  summarise(
    min_raw = min(raw_rating, na.rm = TRUE),
    max_raw = max(raw_rating, na.rm = TRUE)
  )
```

```{r}
#| echo: false
#| warning: false

round_up_table <- ma.2010 %>%
  filter(!is.na(partc_score)) %>%
  mutate(
    round_up = case_when(
      raw_rating >= 2.75 & partc_score == 3.0  ~ "Rounded up to 3",
      raw_rating >= 3.25 & partc_score == 3.5  ~ "Rounded up to 3.5",
      raw_rating >= 3.75 & partc_score == 4.0  ~ "Rounded up to 4",
      raw_rating >= 4.25 & partc_score == 4.5  ~ "Rounded up to 4.5",
      raw_rating >= 4.75 & partc_score == 5.0  ~ "Rounded up to 5",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(round_up)) %>%
  count(round_up) %>%
  rename(`Star Rating` = round_up, `Number of Plans` = n)

print(round_up_table)
```

build raw rating then filter

```{r}
#| include: false
quality_vars <- c(
  "breastcancer_screen",
  "rectalcancer_screen",
  "cv_diab_cholscreen",
  "glaucoma_test",
  "monitoring",
  "flu_vaccine",
  "pn_vaccine",
  "physical_health",
  "mental_health",
  "osteo_test",
  "physical_monitor",
  "primaryaccess",
  "osteo_manage",
  "diab_healthy",
  "bloodpressure",
  "ra_manage",
  "copd_test",
  "bladder",
  "falling",
  "nodelays",
  "doctor_communicate",
  "carequickly",
  "customer_service",
  "overallrating_care",
  "overallrating_plan",
  "complaints_plan",
  "appeals_timely",
  "appeals_review",
  "leave_plan",
  "audit_problems",
  "hold_times",
  "info_accuracy",
  "ttyt_available"
)

datanew.2010 <- data.2010 %>%
  mutate(
    mkt_share = avg_enrollment / avg_enrolled)  %>%
    rowwise() %>%
  mutate(
    raw_rating = mean(c_across(all_of(quality_vars)), na.rm = TRUE)
  ) %>%
  ungroup()
```

```{r}
#| include: false
colnames(datanew.2010)
```

```{r}
#| echo: false
#| warning: false

round_up_counts <- datanew.2010 %>%
  filter(!is.na(raw_rating)) %>%
  filter(!is.na(partc_score)) %>%
  mutate(
    round_ups = case_when(
      raw_rating >= 2.75 & partc_score == 3.0  ~ "Rounded up to 3",
      raw_rating >= 3.25 & partc_score == 3.5  ~ "Rounded up to 3.5",
      raw_rating >= 3.75 & partc_score == 4.0  ~ "Rounded up to 4",
      raw_rating >= 4.25 & partc_score == 4.5  ~ "Rounded up to 4.5",
      raw_rating >= 4.75 & partc_score == 5.0  ~ "Rounded up to 5",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(round_ups)) %>%
  count(round_ups) %>%
  rename('Star Rating' = round_ups, 'Corresponding Number Of Plans' = n)

print(round_up_counts)
```

# Problem 6

```{r}
#| include: false
install.packages("rdrobust")
library(rdrobust)
```

```{r}
#| echo: false
#| warning: false
rd1 <- datanew.2010 %>%
  filter(!is.na(raw_rating), !is.na(mkt_share)) %>%
  mutate(score = raw_rating - 2.75)   # center running variable at cutoff

est1 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.125, p = 1, kernel = "uniform", vce = "hc0")
summary(est1)
```

```{r}
#| echo: false
#| warning: false
rd2 <- datanew.2010 %>%
  filter(!is.na(raw_rating), !is.na(mkt_share)) %>%
  mutate(score = raw_rating - 3.25)   # center running variable at cutoff

est2 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.125, p = 1, kernel = "uniform", vce = "hc0")
summary(est2)
```

```{r}
#| echo: false
#| warning: false
tibble(
  Cutoff   = c("3 Stars vs. 2.5 Stars", "3.5 Stars vs. 3 Stars"),
  Estimate = round(c(est1$coef[1], est2$coef[1]), 4)
) %>% print()
```

# Problem 7

```{r}
#| echo: false
#| warning: false
est0.1 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.1, p = 1, kernel = "uniform", vce = "hc0")
est0.12 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.12, p = 1, kernel = "uniform", vce = "hc0")
est0.13 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.13, p = 1, kernel = "uniform", vce = "hc0")
est0.14 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.14, p = 1, kernel = "uniform", vce = "hc0")
est0.15 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.15, p = 1, kernel = "uniform", vce = "hc0")

results_table_275 <- tibble(
  Bandwidth = c(0.10, 0.12, 0.13, 0.14, 0.15),
  Estimate = c(
    est0.1$coef[1],   # h = 0.10
    est0.12$coef[1],  # h = 0.12
    est0.13$coef[1],  # h = 0.13
    est0.14$coef[1],  # h = 0.14
    est0.15$coef[1]   # h = 0.15
  )
)

print(results_table_275)

ggplot(results_table_275, aes(x = Bandwidth, y = Estimate)) +
  geom_line(size = 1.2, color = "darkred") +
  geom_point(size = 2.5, color = "darkred") +
  labs(
    title = "RD Estimates Across Bandwidths (Cutoff = 2.75)",
    x = "Bandwidth",
    y = "Estimated Jump in Market Share"
  ) +
  theme_minimal()
```

```{r}
#| echo: false
#| warning: false
est3 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.1, p = 1, kernel = "uniform", vce = "hc0")

est4 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.12, p = 1, kernel = "uniform", vce = "hc0")

est5 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.13, p = 1, kernel = "uniform", vce = "hc0")

est6 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.14, p = 1, kernel = "uniform", vce = "hc0")

est7 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.15, p = 1, kernel = "uniform", vce = "hc0")

results_table_325 <- tibble(
  Bandwidth = c(0.10, 0.12, 0.13, 0.14, 0.15),
  Estimate = c(
    est3$coef[1],   # h = 0.10
    est4$coef[1],   # h = 0.12
    est5$coef[1],   # h = 0.13
    est6$coef[1],    # h = 0.14
    est7$coef[1]    # h = 0.15
  )
)

print(results_table_325)

ggplot(results_table_325, aes(x = Bandwidth, y = Estimate)) +
  geom_line(size = 1.2, color = "steelblue") +
  geom_point(size = 2.5, color = "steelblue") +
  labs(
    title = "RD Estimates Across Bandwidths (Cutoff = 3.25)",
    x = "Bandwidth",
    y = "Estimated Jump in Market Share"
  ) +
  theme_minimal()

```

# Problem 8

```{r}
#| echo: false
#| warning: false
plans_3 <- datanew.2010 %>%
  filter(
    !is.na(raw_rating),
    !is.na(partc_score),
    Star_Rating %in% c(2.5, 3)
  )

band_3 <- plans_3 %>%
  filter(
    raw_rating >= 2.5,
    raw_rating <= 3,
    (raw_rating < 2.75  & Star_Rating == 2.5) |
    (raw_rating >= 2.75 & Star_Rating == 3)
  )

rd_3 <- band_3 %>%
  mutate(
    score = raw_rating - 2.75,          
    treat_group = score >= 0,           
    in_window = between(score, -0.125, 0.125),
    interaction = score * treat_group
  )

p_3 <- ggplot(rd_3 %>% filter(in_window),
             aes(x = score, y = mkt_share, color = treat_group)) +
  geom_point(alpha = 0.45, size = 1.4) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.9) +
  scale_color_manual(
    values = c("FALSE" = "#E57373", "TRUE" = "#4F81BD"),
    labels = c("2.5 Stars", "3 Stars")
  ) +
  labs(
    title = "Market Share Around the 2.5 vs 3 Star Cutoff",
    x = "Centered Score (raw rating − 2.75)",
    y = "Market Share",
    color = "Assigned Rating"
  ) +
  theme_minimal()

p_3
```

```{r}
#| echo: false
#| warning: false

plans_3.5 <- datanew.2010 %>%
  filter(
    !is.na(raw_rating),
    !is.na(partc_score),
    Star_Rating %in% c(3, 3.5)
  )

band_3.5 <- plans_3.5 %>%
  filter(
    raw_rating >= 3,
    raw_rating <= 3.5,
    (raw_rating < 3.25  & Star_Rating == 3) |
    (raw_rating >= 3.25 & Star_Rating == 3.5)
  )

rd_3.5 <- band_3.5 %>%
  mutate(
    score = raw_rating - 3.25,          
    treat_group = score >= 0,      
    in_window = between(score, -0.125, 0.125),
    interaction = score * treat_group
  )

p_3.5 <- ggplot(rd_3.5 %>% filter(in_window), 
             aes(x = score, y = mkt_share, color = treat_group)) +
  geom_point(alpha = 0.45, size = 1.4) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.9) +
  scale_color_manual(
    values = c("FALSE" = "#E57373", "TRUE" = "#4F81BD"),
    labels = c("3 Stars", "3.5 Stars")
  ) +
  labs(
    title = "Market Share Around the 3 vs 3.5 Star Cutoff",
    x = "Centered Score (raw rating − 3.25)",
    y = "Market Share",
    color = "Assigned Rating"
  ) +
  theme_minimal()

p_3.5
```

# Problem 9

```{r}
#| echo: false
#| warning: false

near_275 <- datanew.2010 %>%
  mutate(
    score = raw_rating - 2.75,
    group = ifelse(score >= 0, "Above cutoff", "Below cutoff")
  ) %>%
  filter(score >= -0.125, score <= 0.125) %>%
  mutate(
    HMO = str_detect(plan_type, "HMO"),
    PartD = partd == "Yes"
  ) %>%
  group_by(group) %>%
  summarise(
    share_HMO = mean(HMO),
    share_PartD = mean(PartD),
    n = n()
  )

cat("Table: Plan Characteristics Around the 2.75 Cutoff\n")
near_275
```

```{r}
#| echo: false
#| warning: false

near_325 <- datanew.2010 %>%
  mutate(
    score = raw_rating - 3.25,
    group = ifelse(score >= 0, "Above cutoff", "Below cutoff")) %>%
  filter(score >= -0.125, score <= 0.125) %>%
  mutate(
    HMO = str_detect(plan_type, "HMO"),
    PartD = partd == "Yes") %>%
 
group_by(group) %>%
  summarise(
    share_HMO = mean(HMO),
    share_PartD = mean(PartD),
    n = n()
  )

cat("Table: Plan Characteristics Around the 3.25 Cutoff (3–3.5 Stars)\n")
near_325
```

These tables show you whether plans just above each cutoff look similar to plans just below it. Plans just above the 2.75 threshold are completely different types of plans as the ones above are much more likely to be HMOs and to offer Part D. Plans for just above the 3.25 thresold are slightly different but to a lesser degree. 

# Problem 10 

Overall, a higher star rating shows more enrollment but the comparison is compromised as plans above and below the threshold are different. Raw ratings tend to be more distributed around the thresholds (2.75 and 3.25), and the adjusted ratings create jumps in star assignments. Because plan characteristics are distinct and not comparable right above or below the cutoff, the RD model cannot cleanly isolate the effect of the star rating alone. 


