---
title: "Homework 3"
subtitle: "Submission 2, Spring 2026"
author: "Sophie Kim"
format:
  pdf:
    output-file: "Kim-S-hwk3-2"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

```{r}
#| include: false
library(tidyverse)
library(stringr)
library(readr)
library(fs)
library(ggplot2)
library(dplyr)
library(broom)
library(tidyr)
```

```{r}
#| include: false
options(repos = c(CRAN = "https://cloud.r-project.org"))

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, scales, data.table)

install.packages("knitr", lib="~/R/x86_64-conda-linux-gnu-library/4.3")
install.packages("rmarkdown", lib="~/R/x86_64-conda-linux-gnu-library/4.3")
```

```{r}
#| include: false
data.2010 <- read_csv("..//data/data-2010.csv")
data.2011 <- read_csv("..//data/data-2011.csv")
data.2012 <- read_csv("..//data/data-2012.csv")
data.2013 <- read_csv("..//data/data-2013.csv")
data.2014 <- read_csv("..//data/data-2014.csv")
data.2015 <- read_csv("..//data/data-2015.csv")
```

# Problem 1

```{r}
#| include: false
fix_type <- function(df) {
  df$org_parent <- as.character(df$org_parent)
  df
}

data.2011 <- fix_type(data.2011)
```

```{r}
#| include: false
combined <- bind_rows(
  data.2010,
  data.2011,
  data.2012,
  data.2013,
  data.2014,
  data.2015
) %>%
  mutate(mkt_share = avg_enrollment / avg_enrolled)
```

```{r}
#| include: false
colnames(combined)
```



```{r}
#| echo: false
#| warning: false
#| fig-cap: "Mean star rating, number of enrollments, market share for plans by year"
# use star_rating for 1-4 and then use partc_score for 5-10

summary_table <- combined %>%
  group_by(year) %>%
  summarise(
    `Mean Star Rating` = round(mean(Star_Rating, na.rm = TRUE), 2),
    `Mean Enrollments` = round(mean(avg_enrollment, na.rm = TRUE), 2),
    `Mean Market Share` = round(mean(mkt_share, na.rm = TRUE), 4),
    `Total Plans` = n()
  )

print(summary_table)
```

\newpage

# Problem 2

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Mean for plans w/o star rating by year"
summary_no_rating <- combined %>%
  filter(is.na(Star_Rating)) %>%
  group_by(year) %>%
  summarise(
    `Mean Enrollments` = round(mean(avg_enrollment, na.rm = TRUE), 2),
    `Mean Market Share` = round(mean(mkt_share, na.rm = TRUE), 4),
    `Total Plans` = n()
  )

print(summary_no_rating)
```

\newpage

# Problem 3

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Distribution of Star Ratings (2010, 2012, 2015)"

combined %>%
  filter(year %in% c(2010, 2012, 2015), !is.na(Star_Rating)) %>%
  mutate(year = as.factor(year)) %>%
  ggplot(aes(x = as.factor(Star_Rating))) +
  geom_bar() +
  facet_wrap(~ year) +
  labs(
    title = "Distribution of Star Ratings in 2010, 2012, and 2015",
    x = "Star Rating",
    y = "Number of Plans"
  ) +
  theme_minimal()
```

\newpage

# Problem 4

```{r}
#| include: false

combined <- combined %>%
  mutate(
    star_3   = as.integer(Star_Rating == 3),
    star_35  = as.integer(Star_Rating== 3.5),
    star_4   = as.integer(Star_Rating == 4),
    star_45  = as.integer(Star_Rating >= 4.5)
  )

results_list <- list()

for(yr in 2010:2015){
  cat("\nYear:", yr, "\n")
  ols <- lm(mkt_share ~ star_3 + star_35 + star_4 + star_45, 
            data = combined %>% filter(year == yr, !is.na(Star_Rating), !is.na(mkt_share)))
  print(summary(ols))
}
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "OLS Results"

results_list <- list()

for(yr in 2010:2015){
  ols <- lm(mkt_share ~ star_3 + star_35 + star_4 + star_45, 
            data = combined %>% filter(year == yr, !is.na(partc_score), !is.na(mkt_share)))
  results_list[[as.character(yr)]] <- coef(ols)
}

ols_table <- as.data.frame(results_list)
colnames(ols_table) <- c("2010", "2011", "2012", "2013", "2014", "2015")
rownames(ols_table) <- c("Intercept (≤2.5 stars)", "3 Stars", "3.5 Stars", "4 Stars", "4.5+ Stars")

print(round(ols_table, 4))
```

\newpage

# Problem 5


```{r}
#| include: false
quality_vars <- c(
  "breastcancer_screen",
  "rectalcancer_screen",
  "cv_diab_cholscreen",
  "glaucoma_test",
  "monitoring",
  "flu_vaccine",
  "pn_vaccine",
  "physical_health",
  "mental_health",
  "osteo_test",
  "physical_monitor",
  "primaryaccess",
  "osteo_manage",
  "diab_healthy",
  "bloodpressure",
  "ra_manage",
  "copd_test",
  "bladder",
  "falling",
  "nodelays",
  "doctor_communicate",
  "carequickly",
  "customer_service",
  "overallrating_care",
  "overallrating_plan",
  "complaints_plan",
  "appeals_timely",
  "appeals_review",
  "leave_plan",
  "audit_problems",
  "hold_times",
  "info_accuracy",
  "ttyt_available"
)

datanew.2010 <- data.2010 %>%
  mutate(
    mkt_share = avg_enrollment / avg_enrolled)  %>%
    rowwise() %>%
  mutate(
    raw_rating = mean(c_across(all_of(quality_vars)), na.rm = TRUE)
  ) %>%
  ungroup()
```

```{r}
#| include: false
colnames(datanew.2010)
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Number of Plans Rounded Up"
round_up_counts <- datanew.2010 %>%
  distinct(contractid, fips, .keep_all = TRUE) %>%
  filter(!is.na(raw_rating)) %>%
  filter(!is.na(partc_score)) %>%
  mutate(
    round_ups = ifelse(raw_rating >= 2.75 & raw_rating < 3.00 & partc_score == 3.0, "Rounded up to 3",
               ifelse(raw_rating >= 3.25 & raw_rating < 3.5 & partc_score == 3.5, "Rounded up to 3.5",
               ifelse(raw_rating >= 3.75 & raw_rating < 4.0 & partc_score == 4.0, "Rounded up to 4",
               ifelse(raw_rating >= 4.25 & raw_rating < 4.5 & partc_score == 4.5, "Rounded up to 4.5",
               ifelse(raw_rating >= 4.75 & partc_score == 5.0, "Rounded up to 5",
               NA)))))
  ) %>%
  filter(!is.na(round_ups)) %>%
  count(round_ups) %>%
  rename('Star Rating' = round_ups, 'Number Of Plans' = n)

print(round_up_counts)
```

\newpage

# Problem 6

```{r}
#| include: false
run_rd_ols <- function(data, cutoff, stars_below, stars_above) {
  data %>%
    filter(!is.na(raw_rating), !is.na(partc_score),
           partc_score %in% c(stars_below, stars_above)) %>%
    mutate(
      score = raw_rating - cutoff,
      treat = as.integer(score >= 0),
      score_treat = score * treat
    ) %>%
    filter(score >= -0.125, score <= 0.125) %>%
    lm(mkt_share ~ score + treat + score_treat, data = .)
}

star3  <- run_rd_ols(datanew.2010, cutoff = 2.75, stars_below = 2.5, stars_above = 3.0)
star3.5 <- run_rd_ols(datanew.2010, cutoff = 3.25, stars_below = 3.0, stars_above = 3.5)

rename_coefs <- function(mod) {
  s <- summary(mod)
  rownames(s$coefficients) <- c("Intercept", "Running Score", "Rounded", "Running Score x Treat")
  print(s)
}

rename_coefs(star3)
rename_coefs(star3.5)

print (star3)
print (star3.5)
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Estimate of Effects at 3, 3.5 Stars"

results_table <- data.frame(
  Statistic     = c("Intercept", "Rounded", "Running Score", "Num.Obs.", "R2"),
  `3 Stars`     = c(
    round(coef(star3)["(Intercept)"], 3),
    round(coef(star3)["treat"],        3),
    round(coef(star3)["score"],        3),
    nobs(star3),
    round(summary(star3)$r.squared,    3)
  ),
  `3.5 Stars`   = c(
    round(coef(star3.5)["(Intercept)"], 3),
    round(coef(star3.5)["treat"],        3),
    round(coef(star3.5)["score"],        3),
    nobs(star3.5),
    round(summary(star3.5)$r.squared,    3)
  ),
  check.names = FALSE
)

print(results_table, row.names = FALSE)
```

\newpage


# Problem 7

3 stars estimates are stable across all bandwidths, 3.5 estimates are more sensitive to bandwidth choice. Both are relatively robust as the sign of both effects do not change. 

```{r}
#| include: false
install.packages("rdrobust")
library(rdrobust)
```

```{r}
#| include: false
rd1 <- datanew.2010 %>%
  filter(!is.na(raw_rating), !is.na(mkt_share)) %>%
  mutate(score = raw_rating - 2.75)   # center running variable at cutoff


est0.1 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.1, p = 1, kernel = "uniform", vce = "hc0")
est0.12 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.12, p = 1, kernel = "uniform", vce = "hc0")
est0.13 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.13, p = 1, kernel = "uniform", vce = "hc0")
est0.14 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.14, p = 1, kernel = "uniform", vce = "hc0")
est0.15 <- rdrobust(y = rd1$mkt_share, x = rd1$score, c = 0,
                 h = 0.15, p = 1, kernel = "uniform", vce = "hc0")

results_table_275 <- tibble(
  Bandwidth = c(0.10, 0.12, 0.13, 0.14, 0.15),
  Estimate = c(
    est0.1$coef[1],
    est0.12$coef[1],
    est0.13$coef[1],
    est0.14$coef[1],
    est0.15$coef[1]
  ),
  CI_lower = c(
    est0.1$coef[1]  - 1.96 * est0.1$se[1],
    est0.12$coef[1] - 1.96 * est0.12$se[1],
    est0.13$coef[1] - 1.96 * est0.13$se[1],
    est0.14$coef[1] - 1.96 * est0.14$se[1],
    est0.15$coef[1] - 1.96 * est0.15$se[1]
  ),
  CI_upper = c(
    est0.1$coef[1]  + 1.96 * est0.1$se[1],
    est0.12$coef[1] + 1.96 * est0.12$se[1],
    est0.13$coef[1] + 1.96 * est0.13$se[1],
    est0.14$coef[1] + 1.96 * est0.14$se[1],
    est0.15$coef[1] + 1.96 * est0.15$se[1]
  )
)

# print(results_table_275)

ggplot(results_table_275, aes(x = Bandwidth, y = Estimate)) +
  geom_line(size = 1.2, color = "darkred") +
  geom_point(size = 2.5, color = "darkred") +
  geom_ribbon(aes(ymin = CI_lower, ymax = CI_upper), alpha = 0.2, fill = "darkred") +
  scale_y_continuous(breaks = seq(0.00, 0.10, by = 0.01)) +
  labs(
    title = "RD Estimates Across Bandwidths (Cutoff = 2.75)",
    x = "Bandwidth",
    y = "Estimated Jump in Market Share (%)"
  ) +
  theme_minimal()
```

```{r}
#| include: false
rd2 <- datanew.2010 %>%
  filter(!is.na(raw_rating), !is.na(mkt_share)) %>%
  mutate(score = raw_rating - 3.25)   # center running variable at cutoff

est3 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.1, p = 1, kernel = "uniform", vce = "hc0")

est4 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.12, p = 1, kernel = "uniform", vce = "hc0")

est5 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.13, p = 1, kernel = "uniform", vce = "hc0")

est6 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.14, p = 1, kernel = "uniform", vce = "hc0")

est7 <- rdrobust(y = rd2$mkt_share, x = rd2$score, c = 0,
                 h = 0.15, p = 1, kernel = "uniform", vce = "hc0")

results_table_325 <- tibble(
  Bandwidth = c(0.10, 0.12, 0.13, 0.14, 0.15),
  Estimate = c(
    est3$coef[1],
    est4$coef[1],
    est5$coef[1],
    est6$coef[1],
    est7$coef[1]
  ),
  CI_lower = c(
    est3$coef[1]  - 1.96 * est0.1$se[1],
    est4$coef[1] - 1.96 * est0.12$se[1],
    est5$coef[1] - 1.96 * est0.13$se[1],
    est6$coef[1] - 1.96 * est0.14$se[1],
    est7$coef[1] - 1.96 * est0.15$se[1]
  ),
  CI_upper = c(
    est3$coef[1]  + 1.96 * est0.1$se[1],
    est4$coef[1] + 1.96 * est0.12$se[1],
    est5$coef[1] + 1.96 * est0.13$se[1],
    est6$coef[1] + 1.96 * est0.14$se[1],
    est7$coef[1] + 1.96 * est0.15$se[1]
  )
)

# print(results_table_325)

ggplot(results_table_325, aes(x = Bandwidth, y = Estimate)) +
  geom_line(size = 1.2, color = "darkred") +
  geom_point(size = 2.5, color = "darkred") +
  geom_ribbon(aes(ymin = CI_lower, ymax = CI_upper), alpha = 0.2, fill = "darkred") +
  scale_y_continuous(breaks = seq(0.00, 0.10, by = 0.01)) +
  labs(
    title = "RD Estimates Across Bandwidths (Cutoff = 3.25)",
    x = "Bandwidth",
    y = "Estimated Jump in Market Share (%)"
  ) +
  theme_minimal()
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Different Bandwidths"

results_combined <- bind_rows(
  results_table_275 %>% mutate(Cutoff = "2.75"),
  results_table_325 %>% mutate(Cutoff = "3.25")
)

ggplot(results_combined, aes(x = Bandwidth, y = Estimate, color = Cutoff, fill = Cutoff)) +
  geom_line(size = 1.2) +
  geom_point(size = 2.5) +
  geom_ribbon(aes(ymin = CI_lower, ymax = CI_upper), alpha = 0.2, color = NA) +
  scale_color_manual(values = c("2.75" = "darkred", "3.25" = "steelblue")) +
  scale_fill_manual(values = c("2.75" = "darkred", "3.25" = "steelblue")) +
  scale_y_continuous(breaks = seq(-0.10, 0.10, by = 0.01)) +  labs(
    title = "RD Estimates Across Bandwidths",
    x = "Bandwidth",
    y = "Estimated Jump in Market Share (%)",
    color = "Cutoff",
    fill = "Cutoff"
  ) +
  theme_minimal()

# set kernel to uniform so that it's not a weighted mean 
# cutoff +- 0.125, run linear regression within that window
```

\newpage

# Problem 8


```{r}
#| echo: false
#| warning: false
#| fig-cap: "Distribution of Running Rariable Near 2.75 Threshold"

plans_3 <- datanew.2010 %>%
  filter(
    !is.na(raw_rating),
    !is.na(partc_score),
    Star_Rating %in% c(2.5, 3)
  )

band_3 <- plans_3 %>%
  filter(
    raw_rating >= 2.5,
    raw_rating <= 3,
    (raw_rating < 2.75  & Star_Rating == 2.5) |
    (raw_rating >= 2.75 & Star_Rating == 3)
  )

rd_3 <- band_3 %>%
  mutate(
    score = raw_rating - 2.75,          
    treat_group = score >= 0,           
    in_window = between(score, -0.125, 0.125),
    interaction = score * treat_group
  )

p_3 <- ggplot(rd_3 %>% filter(in_window),
             aes(x = score, y = mkt_share, color = treat_group)) +
  geom_point(alpha = 0.45, size = 1.4) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.9) +
  scale_color_manual(
    values = c("FALSE" = "#E57373", "TRUE" = "#4F81BD"),
    labels = c("2.5 Stars", "3 Stars")
  ) +
  labs(
    title = "Market Share Around the 2.5 vs 3 Star Cutoff",
    x = "Centered Score (raw rating − 2.75)",
    y = "Market Share",
    color = "Assigned Rating"
  ) +
  theme_minimal()

p_3
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Distribution of Running Rariable Near 3.25 Threshold"


plans_3.5 <- datanew.2010 %>%
  filter(
    !is.na(raw_rating),
    !is.na(partc_score),
    Star_Rating %in% c(3, 3.5)
  )

band_3.5 <- plans_3.5 %>%
  filter(
    raw_rating >= 3,
    raw_rating <= 3.5,
    (raw_rating < 3.25  & Star_Rating == 3) |
    (raw_rating >= 3.25 & Star_Rating == 3.5)
  )

rd_3.5 <- band_3.5 %>%
  mutate(
    score = raw_rating - 3.25,          
    treat_group = score >= 0,      
    in_window = between(score, -0.125, 0.125),
    interaction = score * treat_group
  )

p_3.5 <- ggplot(rd_3.5 %>% filter(in_window), 
             aes(x = score, y = mkt_share, color = treat_group)) +
  geom_point(alpha = 0.45, size = 1.4) +
  geom_smooth(method = "lm", se = TRUE) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.9) +
  scale_color_manual(
    values = c("FALSE" = "#E57373", "TRUE" = "#4F81BD"),
    labels = c("3 Stars", "3.5 Stars")
  ) +
  labs(
    title = "Market Share Around the 3 vs 3.5 Star Cutoff",
    x = "Centered Score (raw rating − 3.25)",
    y = "Market Share",
    color = "Assigned Rating"
  ) +
  theme_minimal()

p_3.5
```

\newpage

# Problem 9

```{r}
#| echo: false
#| warning: false

near_275 <- datanew.2010 %>%
  mutate(
    score = raw_rating - 2.75,
    group = ifelse(score >= 0, "Above cutoff", "Below cutoff")
  ) %>%
  filter(score >= -0.125, score <= 0.125) %>%
  mutate(
    HMO = str_detect(plan_type, "HMO"),
    PartD = partd == "Yes"
  ) %>%
  group_by(group) %>%
  summarise(
    share_HMO = mean(HMO),
    share_PartD = mean(PartD),
    n = n()
  )

cat("Table: Plan Characteristics Around the 2.75 Cutoff\n")
print(near_275)
```

```{r}
#| echo: false
#| warning: false

near_325 <- datanew.2010 %>%
  mutate(
    score = raw_rating - 3.25,
    group = ifelse(score >= 0, "Above cutoff", "Below cutoff")) %>%
  filter(score >= -0.125, score <= 0.125) %>%
  mutate(
    HMO = str_detect(plan_type, "HMO"),
    PartD = partd == "Yes") %>%
 
group_by(group) %>%
  summarise(
    share_HMO = mean(HMO),
    share_PartD = mean(PartD),
    n = n()
  )

cat("Table: Plan Characteristics Around the 3.25 Cutoff (3–3.5 Stars)\n")
print(near_325)
```

These tables show you whether plans just above each cutoff look similar to plans just below it. Plans just above the 2.75 threshold are completely different types of plans as the ones above are much more likely to be HMOs and to offer Part D. Plans for just above the 3.25 thresold are slightly different but to a lesser degree. 

\newpage

# Problem 10 

Overall, a higher star rating shows more enrollment but the comparison is compromised as plans above and below the threshold are different. Raw ratings tend to be more distributed around the thresholds (2.75 and 3.25), and the adjusted ratings create jumps in star assignments. Because plan characteristics are distinct and not comparable right above or below the cutoff, the RD model cannot cleanly isolate the effect of the star rating alone. 


